Results

### 2024-02-29 Analysis/04_Summarise_results.Rmd
updated MS with simulated 2d/3d data
Needs to finish fancy plot for empirical data

```{r, echo = FALSE}
library(knitr)
## Loading the results
load("../Data/Processed/sim_equalizing.rda")
equalizing <- bkp
load("../Data/Processed/sim_facilitation.rda")
facilitation <- bkp
load("../Data/Processed/sim_filtering.rda")
filtering <- bkp
load("../Data/Processed/sim_competition.rda")
competition <- bkp

@@

```{r, echo = FALSE}
## Creating the list of results
all_results <- list(equalizing   = equalizing,
                    facilitation = facilitation,
                    filtering    = filtering,
                    competition  = competition)

@@

## Re-ordering results for fancyness
new_order <- c(14, 12, 3, 6,
               15, 11, 2, 8,
               7, 4, 5, 13,
               10, 9, 1)
all_results <- lapply(all_results, sort.metrics, order = new_order)

@@

```{r, echo = FALSE}
## Extracting all the scaled results
scaled_results <- extract.table(all_results, scale.method = "between")
scaled_within <- extract.table(all_results, scale.method = "within")
```

@@

```{r, echo = FALSE}
## Slope and R2 for each model
model_fits <- lapply(scaled_results, fit.model.rm)
## Differences between stressor and random
null_differences <- lapply(all_results, paired.tests)

## Making the fancy tables
model_table <- fancy.table(model_fits, columns = list(c(3,4), 5))
null_table <- fancy.table(null_differences, columns = list(c(1,3), c(4, 6), c(7, 9)))
```

```{r, echo = FALSE}
rownames(model_table) <- gsub("\\]", "_", gsub("\\[", "_", gsub("\n", "", fancy_names)))
kable(model_table, caption = "Results of the model scaled metric ~ removal level per stressor", align = "c")
```

```{r, echo = FALSE}
rownames(null_table) <- gsub("\\]", "_", gsub("\\[", "_", gsub("\n", "", fancy_names)))
## Even fancier column names
colnames(null_table) <- gsub(".d_rm", ".rm", colnames(null_table))
colnames(null_table) <- gsub("equalizing", "equa", colnames(null_table))
colnames(null_table) <- gsub("facilitation", "faci", colnames(null_table))
colnames(null_table) <- gsub("filtering", "filt", colnames(null_table))
colnames(null_table) <- gsub("competition", "comp", colnames(null_table))
kable(null_table, caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor", align = "c")
```

@@

```{r, fig.width = 8, fig.height = 10, echo = FALSE}
col_vector <- c(rep("blue", 4), # The richness ones
                rep("orange", 7), # The divergence ones
                rep("darkgreen", 4)) # The regularity ones
## The plot
fancy.plot(scaled_results, col = col_vector, lm = model_fits, null = null_differences, metric.names = fancy_names)

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor.pdf", height = 9, width = 9)
fancy.plot(scaled_results, col = col_vector, lm = model_fits, null = null_differences, metric.names = fancy_names)
dev.off()

@@

>>>>

```{r, echo = FALSE}
library(knitr)
## Loading the results
load("../Data/Processed/sim_equalizing_2d.rda")
equalizing_2d <- bkp
load("../Data/Processed/sim_facilitation_2d.rda")
facilitation_2d <- bkp
load("../Data/Processed/sim_filtering_2d.rda")
filtering_2d <- bkp
load("../Data/Processed/sim_competition_2d.rda")
competition_2d <- bkp

## Loading the results
load("../Data/Processed/sim_equalizing_3d.rda")
equalizing_3d <- bkp
load("../Data/Processed/sim_facilitation_3d.rda")
facilitation_3d <- bkp
load("../Data/Processed/sim_filtering_3d.rda")
filtering_3d <- bkp
load("../Data/Processed/sim_competition_3d.rda")
competition_3d <- bkp

## Loading empirical results
load("../Data/Processed/empirical_data-hist-present-native.rda")
empirical_hist <- bkp
load("../Data/Processed/empirical_data-prehist-present-native.rda")
empirical_prehist <- bkp

hist_table <- empirical_hist$results_table
colnames(hist_table) <- gsub("_rm1", "_rm2", colnames(hist_table))
combined_empirical <- list()
combined_empirical$results_table <- cbind(empirical_prehist$results_table, hist_table)

@@

```{r, echo = FALSE}
## Creating the list of results
all_results_2d <- list(equalizing   = equalizing_2d,
                       facilitation = facilitation_2d,
                       filtering    = filtering_2d,
                       competition  = competition_2d)
all_results_3d <- list(equalizing   = equalizing_3d,
                       facilitation = facilitation_3d,
                       filtering    = filtering_3d,
                       competition  = competition_3d)
empirical_results <- list(combined_empirical)

@@

## Re-ordering results for fancyness
new_order <- c(14, 12, 3, 6,
               15, 11, 2, 8,
               7, 4, 5, 13,
               10, 9, 1)
all_results_2d <- lapply(all_results_2d, sort.metrics, order = new_order)
all_results_3d <- lapply(all_results_3d, sort.metrics, order = new_order)
empirical_results <- lapply(empirical_results, sort.metrics, order = new_order)

@@

```{r, echo = FALSE}
## Extracting all the scaled results
scaled_results_2d <- extract.table(all_results_2d, scale.method = "between")
scaled_within_2d  <- extract.table(all_results_2d, scale.method = "within")
scaled_results_3d <- extract.table(all_results_3d, scale.method = "between")
scaled_within_3d  <- extract.table(all_results_3d, scale.method = "within")
scaled_results_emp<- extract.table(empirical_results, scale.method = "between")
scaled_within_emp <- extract.table(empirical_results, scale.method = "within")
```

@@

```{r, echo = FALSE}
## Slope and R2 for each model
model_fits_2d  <- lapply(scaled_results_2d, fit.model.rm)
model_fits_3d  <- lapply(scaled_results_3d, fit.model.rm)
model_fits_emp <- lapply(scaled_results_emp, fit.model.rm)

## Differences between stressor and random
null_differences_2d  <- lapply(all_results_2d, paired.tests)
null_differences_3d  <- lapply(all_results_3d, paired.tests)
null_differences_emp <- lapply(empirical_results, paired.tests)

## Making the fancy tables
model_table_2d  <- fancy.table(model_fits_2d, columns = list(c(3,4), 5))
model_table_3d  <- fancy.table(model_fits_3d, columns = list(c(3,4), 5))
model_table_emp <- fancy.table(model_fits_emp, columns = list(c(3,4), 5))
null_table_2d   <- fancy.table(null_differences_2d, columns = list(c(1,3), c(4, 6), c(7, 9), c(10, 12)))
null_table_3d   <- fancy.table(null_differences_3d, columns = list(c(1,3), c(4, 6), c(7, 9), c(10, 12)))
null_table_emp  <- fancy.table(null_differences_emp, columns = list(c(1,3), c(4, 6)))
```

```{r, echo = FALSE}
rownames(model_table_2d) <- gsub("\\]", "_", gsub("\\[", "_", gsub("\n", "", fancy_names)))
kable(model_table_2d, caption = "Results of the model scaled metric ~ removal level per stressor (2D)", align = "c")
```
```{r, echo = FALSE}
rownames(model_table_3d) <- gsub("\\]", "_", gsub("\\[", "_", gsub("\n", "", fancy_names)))
kable(model_table_3d, caption = "Results of the model scaled metric ~ removal level per stressor (3D)", align = "c")
```
```{r, echo = FALSE}
rownames(model_table_emp) <- gsub("\\]", "_", gsub("\\[", "_", gsub("\n", "", fancy_names)))
kable(model_table_emp, caption = "Results of the model scaled metric ~ removal level for the empirical data (3D)", align = "c")
```
```{r, echo = FALSE}
rownames(null_table_2d) <- gsub("\\]", "_", gsub("\\[", "_", gsub("\n", "", fancy_names)))
## Even fancier column names
colnames(null_table_2d) <- gsub(".d_rm", ".rm", colnames(null_table_2d))
colnames(null_table_2d) <- gsub("equalizing", "equa", colnames(null_table_2d))
colnames(null_table_2d) <- gsub("facilitation", "faci", colnames(null_table_2d))
colnames(null_table_2d) <- gsub("filtering", "filt", colnames(null_table_2d))
colnames(null_table_2d) <- gsub("competition", "comp", colnames(null_table_2d))
kable(null_table_2d, caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (2d)", align = "c")
```

```{r, echo = FALSE}
rownames(null_table_3d) <- gsub("\\]", "_", gsub("\\[", "_", gsub("\n", "", fancy_names)))
## Even fancier column names
colnames(null_table_3d) <- gsub(".d_rm", ".rm", colnames(null_table_3d))
colnames(null_table_3d) <- gsub("equalizing", "equa", colnames(null_table_3d))
colnames(null_table_3d) <- gsub("facilitation", "faci", colnames(null_table_3d))
colnames(null_table_3d) <- gsub("filtering", "filt", colnames(null_table_3d))
colnames(null_table_3d) <- gsub("competition", "comp", colnames(null_table_3d))
kable(null_table_3d, caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (3d)", align = "c")
```

```{r, echo = FALSE}
rownames(null_table_emp) <- gsub("\\]", "_", gsub("\\[", "_", gsub("\n", "", fancy_names)))
## Even fancier column names
colnames(null_table_emp) <- gsub(".d_rm", ".rm", colnames(null_table_emp))
colnames(null_table_emp) <- gsub("equalizing", "equa", colnames(null_table_emp))
colnames(null_table_emp) <- gsub("facilitation", "faci", colnames(null_table_emp))
colnames(null_table_emp) <- gsub("filtering", "filt", colnames(null_table_emp))
colnames(null_table_emp) <- gsub("competition", "comp", colnames(null_table_emp))
kable(null_table_emp, caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal for the empirical data (pre-history and history)", align = "c")
```

@@

```{r, fig.width = 8, fig.height = 10, echo = FALSE}
col_vector <- c(rep("blue", 4), # The richness ones
                rep("orange", 7), # The divergence ones
                rep("darkgreen", 4)) # The regularity ones
## The plot
fancy.plot(scaled_results_2d, col = col_vector, lm = model_fits_2d, null = null_differences_2d, metric.names = fancy_names)

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_2d.pdf", height = 9, width = 9)
fancy.plot(scaled_results_2d, col = col_vector, lm = model_fits_2d, null = null_differences_2d, metric.names = fancy_names)
dev.off()
```

@@

```{r}
## The plot
fancy.plot(scaled_results_3d, col = col_vector, lm = model_fits_3d, null = null_differences_3d, metric.names = fancy_names)

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_3d.pdf", height = 9, width = 9)
fancy.plot(scaled_results_3d, col = col_vector, lm = model_fits_3d, null = null_differences_3d, metric.names = fancy_names)
dev.off()
```

```{r}
## The plot
fancy.plot(scaled_results_emp, col = col_vector, lm = model_fits_emp, null = null_differences_emp, metric.names = fancy_names)

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_emp.pdf", height = 9, width = 9)
fancy.plot(scaled_results_emp, col = col_vector, lm = model_fits_emp, null = null_differences_emp, metric.names = fancy_names)
dev.off()
```
